---
title: "Research Paper"
author: "Anil Battalahalli Sreenath"
date: "4/22/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("GGally")
library(ggplot2)
library(dplyr)
library(boot)
library(gridExtra)
library(parallel)
library(vegan)
library(cluster)
library(coin)
options(warn=-1)
set.seed(84884)
```

```{r}
cl <- makeCluster(detectCores())
```

```{r}
df <- read.csv('absolute_grand_final.csv')
df$unef <- ifelse(df$unemp <= 6, TRUE, FALSE)
df$hdif <- ifelse(df$HDI >= 0.55, TRUE, FALSE)
df$intf <- ifelse(df$Year >= 2010, TRUE, FALSE)
df$gdppcf <- ifelse(df$GDP >=3000, TRUE, FALSE)
```

Select Columns for Pair Plot:

```{r}
df_num <- subset(df, select = -c(Country, unef, hdif, intf, gdppcf))
ggcorr(
  df_num,
  geom = "tile",
  max_size = 6,
  size = 3.5,
  hjust = 0.75,
  #angle = -45, 
  color = "grey50",
  label = TRUE,
  label_size = 3, 
  label_round = 2, 
  label_alpha = TRUE,
  palette = ""
)
```

```{r, message=FALSE, warning=FALSE}
a <- ggplot(df, aes(x = HDI, color = hdif, fill = hdif)) + geom_density(alpha = 0.5)+theme_minimal()+xlab("HDI")
b <- ggplot(df, aes(x = GDP, color = hdif, fill = hdif)) + geom_density(alpha = 0.5)+xlim(c(0, 20000))+xlab("GDP Per Capita")+theme_minimal()
c <- ggplot(df, aes(x = pop, color = hdif, fill = hdif)) + geom_density(alpha = 0.5)+xlim(c(0, 1000000))+xlab("Population")+theme_minimal()
d <- ggplot(df, aes(x = unemp, color = hdif, fill = hdif)) + geom_density(alpha = 0.5)+xlab("Unemployment Rate")+theme_minimal()
grid.arrange(a, b, c, d, nrow=2, ncol=2)
```

**Research Questions:**

1.  Do bipolar disorder and anxiety disorders coexist? Bootstrap
2.  What is the mean difference in the mental illnesses and the suicide rates in developed and underdeveloped countries? Bootstrap


### 1. Is there any evidence that the mental illness rates for different illnesses are correlated? Using Bootstrap

```{r, message=FALSE, warning=FALSE}
a <- ggplot(df, aes(x = bipolar_perc)) + geom_density(alpha = 0.5)+theme_minimal()+xlab("Bipolar Disorder")+ylab("Density")
b <- ggplot(df, aes(x = anxiety_perc)) + geom_density(alpha = 0.5)+xlab("Anxiety")+ylab("Density")+theme_minimal()
c <- ggplot(df, aes(x = schiz_perc)) + geom_density(alpha = 0.5)+xlab("Schizophrenia")+ylab("Density")+theme_minimal()
d <- ggplot(df, aes(x = depr_perc)) + geom_density(alpha = 0.5)+xlab("Depression")+ylab("Density")+theme_minimal()
grid.arrange(a, b, c, d, nrow=2, ncol=2)
```

```{r}
dis <- c("schiz_perc", "bipolar_perc", "anxiety_perc", "depr_perc")
c <- t(combn(dis,2))
```

```{r}
for (i in dis){
  print(i)
  print(shapiro.test(as.numeric(unlist(df[i]))))
  print("---------------------------------")
}
```


```{r}
for (i in 1:dim(c)[1]){
  print(independence_test(as.formula(paste(c[i,1], '~' , c[i,2])), df, distribution = approximate(10000)))
}
```

```{r}
get_corr <- function(x, index){
  a = names(x)[1]
  b = names(x)[2]
  x_sample <- x[index,]
  return(cor(x_sample[a],x_sample[b]))
}

do_boot <- function(x){
  print(names(x))
  boot_corr <- boot(x, statistic = get_corr, R = 1000, parallel = 'snow', cl=cl)
  print(boot.ci(boot_corr, type = c("basic"), conf = 0.95))
  cat("\n\n")
}
```

```{r}
for (i in 1:dim(c)[1]){
  do_boot(df[c[i,]])
}
```
``

###Are the growth metrics correlated? Bootstrapping

```{r}
dis <- c("pop", "GDP", "HDI")
c <- t(combn(dis,2))
```

```{r}
get_corr <- function(x, index){
  a = names(x)[1]
  b = names(x)[2]
  x_sample <- x[index,]
  return(cor(x_sample[a],x_sample[b]))
}

do_boot <- function(x){
  print(names(x))
  boot_corr <- boot(x, statistic = get_corr, R = 1000, parallel = 'snow', cl=cl)
  print(boot.ci(boot_corr, type = c("basic"), conf = 0.95))
  cat("\n\n")
}
```

```{r}
for (i in 1:dim(c)[1]){
  do_boot(df[c[i,]])
}
```

### 2.  What is the mean difference in the mental illnesses and the suicide rates in developed and underdeveloped countries? Bootstrap

### HDI BASED:

```{r}
names(df)
```
```{r}
valcol <- c("schiz_perc","bipolar_perc","anxiety_perc","drug_perc","depr_perc","alc_perc","suicide_tt")
```

```{r}
ggplot(df[df$Year == 2000,], aes(GDP,HDI,color=hdif)) + geom_point(size = 0.1, stroke = 0, shape = 16) + geom_text(aes(label=Country), size=3)+theme_minimal()
```

```{r}
a <- ggplot(df, aes(x = bipolar_perc, color = hdif, fill = hdif)) + geom_density(alpha = 0.5)+theme_classic()
b <- ggplot(df, aes(x = schiz_perc, color = hdif, fill = hdif)) + geom_density(alpha = 0.5)+theme_classic()
c <- ggplot(df, aes(x = anxiety_perc, color = hdif, fill = hdif)) + geom_density(alpha = 0.5)+theme_classic()
d <- ggplot(df, aes(x = depr_perc, color = hdif, fill = hdif)) + geom_density(alpha = 0.5)+theme_classic()
grid.arrange(a, b, c, d, nrow=2, ncol=2)
```

```{r}
ggplot(df, aes(x = suicide_tt, fill = hdif)) + geom_density(alpha = 0.5)+theme_classic()
```




### CLUSTER BASED:
```{r}
u <- df %>% select(c("Year","GDP","HDI","unef","hdif","intf","gdppcf","pop")) %>% 
      mutate_if(is.numeric, scale) %>% 
      vegdist(method = "gower") %>% 
      pam(k=2, diss=TRUE) 
```

```{r}
df$strata <- ifelse(u$clustering == 1, yes=TRUE, no=FALSE)
```

```{r}
ggplot(df[df$Year == 2000,], aes(GDP,HDI,color=strata)) + geom_point(size = 0.1, stroke = 0, shape = 16) + geom_text(aes(label=Country), size=3)
```

### Plotting all the good things

```{r, message=FALSE, warning=FALSE}
a <- ggplot(df, aes(x = HDI, color = strata, fill = strata)) + geom_density(alpha = 0.5)+theme_classic()
b <- ggplot(df, aes(x = GDP, color = strata, fill = strata)) + geom_density(alpha = 0.5)+xlim(c(0, 20000))+theme_classic()
c <- ggplot(df, aes(x = pop, color = strata, fill = strata)) + geom_density(alpha = 0.5)+theme_classic()+xlim(c(0, 1000000))
d <- ggplot(df, aes(x = unemp, color = strata, fill = strata)) + geom_density(alpha = 0.5)+theme_classic()
grid.arrange(a, b, c, d, nrow=2, ncol=2)
```

### Plotting all the illnesses

```{r}
a <- ggplot(df, aes(x = bipolar_perc, color = strata, fill = strata)) + geom_density(alpha = 0.5)+theme_classic()
b <- ggplot(df, aes(x = schiz_perc, color = strata, fill = strata)) + geom_density(alpha = 0.5)+theme_classic()
c <- ggplot(df, aes(x = anxiety_perc, color = strata, fill = strata)) + geom_density(alpha = 0.5)+theme_classic()
d <- ggplot(df, aes(x = depr_perc, color = strata, fill = strata)) + geom_density(alpha = 0.5)+theme_classic()
grid.arrange(a, b, c, d, nrow=2, ncol=2)
```
Plotting suicides

```{r}
ggplot(df, aes(x = suicide_tt, fill = strata)) + geom_density(alpha = 0.5)+theme_classic()
```

Difference between FALSE (developed) and TRUE (underdeveloped)

```{r}
get_meandiff <- function(x, index, a){
  x_sample <- x[index,]
  return(mean(as.matrix(x_sample[!x_sample$strata,][a]))-mean(as.matrix(x_sample[x_sample$strata,][a])))
}

valcol <- c("schiz_perc","bipolar_perc","anxiety_perc","drug_perc","depr_perc","alc_perc","suicide_tt")

for (i in valcol){
  print(i)
  boot_corr <- boot(df, statistic = get_meandiff, a = i, R = 1000, parallel = 'snow', cl=cl)
  print(boot.ci(boot_corr, type = c("basic"), conf = 0.95))
  cat("\n\n")
}
```
